### 2023-11-07 README.Rmd
Amended plotmultflags to accept sauout rather than zoneDP.
Enabled upliH and incH to be varied by jurisdiction. No EWN

@@

>>>>

* 2023-11-07 aMSE 0.1.15 Generalized the estimation of productivity to allow for alternative values of the starting H and upper limit to H to be applied to the dynamics while searching for the productivity curves. The production matrix is also used by dodepletion, so uplimH values > 0.4 were required (by SA). Only a small cahnge is now required in do_MSE, see the respective help.

@@

* 2023-10-18 aMSE 0.1.14 A catch-up event where I have added some population level plots, I have fixed up the use of plotmultflags so that the exploitable biomass depletion plots really are at the sau level bu changing the input expected.
